PIK3CA mutation prediction

### 2020-04-02 pancancer.Rmd
success run without parallel processing
coeff

---
title: "PIK3CA mutation prediction"
output: "html_document"
bibliography: bibliography.bib
---

@@

Breast cancer with PIK3CA mutation has been approved to use PIK3CA inhibitor in hormone receptor positive HER2 negative subtype. Prediction of PIK3CA mutation was done by gene expression data of TCGA.[]

@@

### Dataset

@@

Penalized logistic regression was applied to prediction modeling. 10-fold cross-validation with targe variable stratification was done over the hyperparameter grid: $\lambda$ {$10^{-5}$, $10^{-4}$,$10^{-3}$,$10^{-2}$,$10^{-1}$, $10^{0}$}, $\alpha$ {0.0, 0.25, 0.5, 0.75}. Model performance was evealuated with the receiver operating characteristic (AUROC).

The model showed best performance at lambda = 0.01 and alpha = 1.0 (Ridge regression).

@@

>>>>

---
title: "PIK3CA mutation prediction"
output: "github_document"
bibliography: references.bib
---

@@

Breast cancer with PIK3CA mutation has been approved to use PIK3CA inhibitor in hormone receptor positive HER2 negative subtype. Prediction of PIK3CA mutation was done by gene expression data of TCGA.

@@

RNAseq can be widely used. The mutation status directly predictio
### Dataset

@@

Penalized logistic regression was applied to prediction modeling. 10-fold cross-validation with targe variable stratification was done over the hyperparameter grid: $\lambda$ {$10^{-5}$, $10^{-4}$,$10^{-3}$,$10^{-2}$,$10^{-1}$, $10^{0}$}, $\alpha$ {0.0, 0.25, 0.5, 0.75}. Model performance was evealuated with the area under receiver operating characteristic (ROC) and area under the ROC (AUROC) and precision recall (PR) and area under curve (AUPR).

@@

## Results

### selecting model
Cross-validation 
The model showed best performance at lambda = 0.01 and alpha = 1.0 (Ridge regression).

### Prediction performance

#### performance of each cancer type

#### Important predictors
